### 2023-02-12 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_interpreting_probabilities@e2e56a3bd52288cdebb8b5b7975ec80364fd35a7 🚀

Metawebs and local networks intrinsically differ in their relation to
scale. On one hand, as mentioned above, probabilistic metawebs are
context independent, i.e., probabilistic pairwise interactions do not
scale with space and time because they depend solely on the biological
capacity of the two taxa to interact. This implies that the estimated
likelihood that two species can potentially interact should be the same
among all metawebs in which they are present. In practice, this is
rarely the case because ecologists use different methods and data to
estimate these probabilities of interactions. However, in the case where
local metawebs \(M_{x,y}\) are subsampled from their regional
counterpart \(M_0\), we should expect edge values to be identical among
all networks, regardless of their spatial scale,
i.e.~\(P_{M_{x,y}}(i \rightarrow j) = P_{M_0}(i \rightarrow j)\). On the
other hand, local probabilistic networks are indissociable from their
spatial and temporal contexts because there are more opportunities of
interactions (e.g., more individuals, more trait variations, more chance
of encounter) in a larger area and longer time period (McLeod \emph{et
al.} 2020). Let \(N_0\) be a local probabilistic food web delineated in
an area \(A_0\) and \(N_1\) a network of area \(A_1 < A_0\) within
\(A_0\). We should expect the probability that \(i\) and \(j\) interacts
to scale spatially, i.e.
\(P_{N_1}(i \rightarrow j | A < A_0) \le P_{N_0}(i \rightarrow j | A = A_0)\).
Similarly, the temporal scaling of probabilistic local food webs could
be manifested through the effect of sampling effort on the observation
of interactions (McLeod \emph{et al.} 2021;
\textbf{Jordano2016Samplinga?}) or of time itself on their realization
(Poisot \emph{et al.} 2012). There are many network-area relationships
(e.g., Wood \emph{et al.} 2015; Galiana \emph{et al.} 2018) and
interaction accumulation curves (e.g, \textbf{Jordano2016Samplinga?})
explored in the literature. These could inspire the development and
testing of different equations describing the spatiotemporal scaling of
probabilistic pairwise interactions in local networks, which are over
the scope of this manuscript.

@@

>>>>

Metawebs and local networks intrinsically differ in their relation to
scale. On one hand, as mentioned above, probabilistic metawebs are
context independent, i.e., probabilistic pairwise interactions do not
scale with space and time because they depend solely on the biological
capacity of the two taxa to interact. This implies that the estimated
likelihood that two species can potentially interact should be the same
among all metawebs in which they are present. In practice, this is
rarely the case because ecologists use different methods and data to
estimate these probabilities of interactions. However, in the case where
local metawebs \(M_{x,y}\) are subsampled from their regional
counterpart \(M_0\), we should expect edge values to be identical among
all networks, regardless of their spatial scale,
i.e.~\(P_{M_{x,y}}(i \rightarrow j) = P_{M_0}(i \rightarrow j)\). On the
other hand, local probabilistic networks are indissociable from their
spatial and temporal contexts because there are more opportunities of
interactions (e.g., more individuals, more trait variations, more chance
of encounter) in a larger area and longer time period (McLeod \emph{et
al.} 2020). Let \(N_0\) be a local probabilistic food web delineated in
an area \(A_0\) and \(N_1\) a network of area \(A_1 < A_0\) within
\(A_0\). We should expect the probability that \(i\) and \(j\) interacts
to scale spatially, i.e.
\(P_{N_1}(i \rightarrow j | A < A_0) \le P_{N_0}(i \rightarrow j | A = A_0)\).
Similarly, the temporal scaling of probabilistic local food webs could
be manifested through the effect of sampling effort on the observation
of interactions (Jordano 2016; McLeod \emph{et al.} 2021) or of time
itself on their realization (Poisot \emph{et al.} 2012). There are many
network-area relationships (e.g., Wood \emph{et al.} 2015; Galiana
\emph{et al.} 2018) and interaction accumulation curves (e.g, Jordano
2016) explored in the literature. These could inspire the development
and testing of different equations describing the spatiotemporal scaling
of probabilistic pairwise interactions in local networks, which are over
the scope of this manuscript.

@@

\leavevmode\hypertarget{ref-Jordano2016SamNet}{}%
Jordano, P. (2016). Sampling networks of ecological interactions.
\emph{Functional Ecology}, 30, 1883--1893.
